### 2016-04-12 outline.tex
fill out notes on start of model

\vskip.5in
\section{Median Legislator's Condition}
\begin{itemize}
	\item I believe I have to change the legislature's condition to be more like the cheater's payoff for this context
		\[
		  W_{ML}\left( \tau^{AD},\tau^{*a},\ga(e,\ta)\right) > W_{ML}\left( \bta,\ga(e,\ta)\right)
		\]
		\begin{itemize}
			\item Need to make sure this is not always the case.
				\begin{itemize}
					\item Median legislator still has to balance (weighted) producers and consumers.
					\item If $\ga = 1$, would pick optimal tariff.
					\item If $\ga$ is so low that $\tau^N < \tau^a$, then agreement will hold. If $\tau^a < \tau^{AD} < \tau^{AD}$, depends on which is closer in welfare terms 
				\end{itemize}
			\item Seems to work okay in Matlab example: just pushes up break probability, trade agreement tariff; reduces gamma and effort (``SOP$\_$example.m'')
			\item Need to check exec's SOC
		\end{itemize}
	\item There could also be uncertainty about the probability that foreign will dispute the AD measure; that could change from the original to the renewal
\end{itemize}

@@

\newpage
\section{Model}
What are the \textit{essential} insights I want to capture?

>>>>

\vskip.5in
\section{Median Legislator's Condition}
\begin{itemize}
	\item I believe I have to change the legislature's condition to be more like the cheater's payoff for this context
		\[
		  W\left( \tau^{AD},\tau^{*a},\ga(e,\ta)\right) > W\left( \bta,\ga(e,\ta)\right)
		\]
		\begin{itemize}
			\item Need to make sure this is not always the case.
				\begin{itemize}
					\item Median legislator still has to balance (weighted) producers and consumers.
					\item If $\ga = 1$, would pick optimal tariff.
					\item If $\ga$ is so low that $\tau^N < \tau^a$, then agreement will hold. If $\tau^a < \tau^{AD} < \tau^{AD}$, depends on which is closer in welfare terms 
				\end{itemize}
			\item Seems to work okay in Matlab example: just pushes up break probability, trade agreement tariff; reduces gamma and effort (``SOP$\_$example.m'')
			\item Need to check exec's SOC
		\end{itemize}
	\item There could also be uncertainty about the probability that foreign will dispute the AD measure; that could change from the original to the renewal
\end{itemize}

@@

\newpage
\section{Model}
What are the \textit{essential} insights/predictions I want to capture?
\begin{enumerate}
	\item uncertainty about ITC's preferences impacts lobby's incentives to exert effort
	\item cross-industry variation in whether AD duties are renewed
\end{enumerate}

\vskip.2in
Do I need two stages? What happens with only one stage?
\begin{enumerate}
	\item Given $\tau^{AD}$, lobby chooses $e$
	\item $\ta$ realized
	\item ITC decides between $\tau^{AD}$ and $\tau^a$ using
	  \[
		  W\left(\ga(e,\ta), \tau^{AD},\tau^{*a}\right) > W\left(\ga(e,\ta), \tau^a, \tau^{*a}\right)
		\]
\end{enumerate}

\vskip.2in
This is simple because there's only one lobby, action in only one country
\begin{itemize}
	\item Although there may be pressure from foreign
	\item Or in a three-country model: third country benefits from discrimination against foreign $\left( * \right)$
\end{itemize}

\vskip1in
Next steps:
\begin{enumerate}
	\item Check BS GE model
	\item Check on how results from JMP would translate given no punishments
	\item How do I make this vary across industry? $\pi$ function, $\ga$, $\ta$, $\tau^a$, $\tau^{AD}$
\end{enumerate}
